---
title: "OxCGRT analysis"
output: html_notebook
---

Start by bringing in packages.

```{r}
# global vars
days_lead <- 7
days_lag <- 0
R_est_window <- 2
```


```{r}
library(tidyverse)
library(plm)
library(magrittr)
library(oxcgrt)
library(zoo)
library(EpiEstim)
library(imputeTS)
```

Load in data and process it.

```{r}
files <- c('Confidence_The_Civil_Services.csv',
           'Confidence_Justice_SystemCourts.csv',
           'Confidence_The_Police.csv')

dfs <- map(files, ~read_csv(.x) %>%
             select(-X1) %>%
             t() %>%
             as.data.frame.matrix
           )

column_names <- c('A_great_deal',
                  'Quite_a_lot',
                  'Not_very_much',
                  'None_at_all',
                  'Do_not_know')

names(dfs[[1]]) <- column_names
names(dfs[[2]]) <- column_names
names(dfs[[3]]) <- column_names

dfs2 <- dfs %>%
  map(function (x) { #x %<>%
        # select(-Do_not_know)
    
        x$Total <- rowSums(x)
        
        x %<>%
          transmute(
            A_great_deal_num = (A_great_deal * 4) / Total,
            Quite_a_lot_num = (Quite_a_lot * 3 ) / Total,
            Not_very_much_num = (Not_very_much * 2 ) / Total,
            None_at_all_num = (None_at_all) / Total
          )

        x %<>% rowSums()
        
        x
  }
  )

dfs3 <- reduce(dfs2, bind_rows) %>%
  t() %>%
  as.data.frame.matrix() %>%
  rowMeans() %>%
  as.data.frame %>% 
  rownames_to_column('country')

names(dfs3) <- c('country', 'govt_trust')
```


Get OxCGRT data

```{r}
oxcgrt_selector <- get_json_time(from = "2020-01-01", 
                 to = "2020-12-31")

oxcgrt_data <- oxcgrt_selector %>% get_data_time()
```

Get GDP data

```{r}
gdp <- read_csv('GDP.csv')
```

Population data

```{r}
pop <- read_csv('population.csv')
```



Join datasets

```{r}
european <- c("Albania", "Andorra", "Austria", "Bosnia & Herzegovina", "Bulgaria", "Croatia", "Cyprus", "Czechia", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Iceland", "Italy", "Lithuania", "Netherlands", "Norway", "Poland", "Portugal", "Romania", "Russia", "Serbia", "Slovakia", "Slovenia", "Spain", "Sweden", "Switzerland", "Ukraine","United Kingdom")

country_key <- read_csv('countries.csv')

names(country_key) <- c('country', 'country_name')

combined_data <- dfs3 %>%
  left_join(country_key) %>%
  right_join(oxcgrt_data) %>%
  left_join(gdp) %>%
  left_join(pop, by = 'country_code') #%>%
  # filter(country_name %in% european)
```

```{r}
combined_data %<>%
  group_by(country_code) %>%
  select(-pop2018) %>%
  mutate(incidence = confirmed - dplyr::lag(confirmed),
         inc_pop = incidence / pop2019,
         inc_pop_4da = zoo::rollmean(inc_pop, k = 4, fill = NA, align = 'right'),
        t = as.POSIXct(date_value),
        t = as.Date(t))
no_missing <- combined_data[complete.cases(combined_data),]

no_missing[no_missing$incidence < 0, 'incidence'] <- NA

no_missing %<>%
  # group_by(country_code) %>%
  imputeTS::na_locf(na_remaining = "rev")
```

Remove missing and impute where we've removed negative cases to last observation.

Filter from first day with 100+ cases, impute missing days with previous value


Get R value estimate
```{r, warning = FALSE}
R_results_list <- list()

no_missing$R_est <- NA
for (i in 1:length(unique(no_missing$country_code)))   {
    index_code <- unique(no_missing$country_code)[i]
    country_incidence <-  no_missing$incidence[no_missing$country_code == index_code]
    
    T <- length(country_incidence)

  t_start <- seq(2, T - R_est_window) # starting at 2 as conditional on the past observations
  t_end <- t_start + R_est_window # adding 2 to get 3-day windows as bounds included in window
    
    R_ests <- estimate_R(country_incidence,
             method="parametric_si",
             config = make_config(list(
               mean_si = 4.8,
               std_si = 2.3,
               t_start = t_start,
               t_end = t_end))
             )

    # plot(R_ests)

    # Get R spreadsheet and add in proper dates
    R_ests <- R_ests$R[complete.cases(R_ests$R),]
    R_ests$date_value <- no_missing$date_value[R_ests$t_start]

    R_results_list[[index_code]] <- R_ests
  }

R_results <- bind_rows(R_results_list, .id = "country_code")
```



```{r}
final_data <- left_join(no_missing, R_results, by = c('date_value', "country_code")) %>%
  mutate(future_effect = (dplyr::lead(`Mean(R)`, days_lead) - dplyr::lag(`Mean(R)`, days_lag)) / -dplyr::lag(`Mean(R)`, days_lag),
stringency_change = stringency - dplyr::lag(stringency)) %>%
  imputeTS::na_locf(na_remaining = "rev")

final_data$R_est <- final_data$`Mean(R)`

# Test just looking at changes
# Added only stringency increases
final_data %<>%
filter(stringency > dplyr::lag(stringency)) %>%
mutate(next_change = dplyr::lead(t) - t,
      last_change = t - dplyr::lag(t)) %>%
filter(last_change >= 7, next_change >= 7)
```
Remove any data before case 100 (as an experiment).

```{r}
final_data_100 <- final_data %>%
  filter(confirmed >= 100)
```


```{r}
model <- plm(future_effect ~ stringency_change + inc_pop_4da + log(GDP) + log(Density) + govt_trust  + stringency_change * govt_trust,
            data = final_data_100, model = "random", effect = "individual",
            index = c("country_code"))
```

```{r}
summary(model)
```

Get correlations to understand this effect.


```{r}
R_plots <- final_data_100$country_code %>%
  unique() %>%
  map(~filter(final_data_100, country_code == .x) %>%
    ggplot(aes(x = t, R_est)) +
      geom_line(colour = 'red') +
      geom_line(aes(y = stringency / 20), colour = 'blue') + 
      facet_wrap(vars(country_code))
  )
```

```{r}
R_cors <- final_data_100$country_code %>%
  unique() %>%
  map(~filter(final_data_100, country_code == .x) %>%
    ungroup() %>%
    select(stringency, R_est, govt_trust) %>%
    cor(use = "pairwise.complete.obs"))

for (i in 1:length(R_cors)) {
  R_cors[[i]] <- R_cors[[i]][1,2]
}

R_cors %<>% unlist
```


```{r}
final_data_100 %>%
    group_by(country_code) %>%
    summarise(meanR = mean(R_est), govt = mean(govt_trust)) %>%
    ggplot(aes(meanR, govt)) +
        geom_point()

final_data_100 %>%
    group_by(country_code) %>%
    summarise(meanR = mean(R_est), meanString = mean(stringency)) %>%
    ggplot(aes(meanR, meanString)) +
        geom_point()
```

```{r}
lebanon <- no_missing %>% 
  filter(country_code == 'LBN') %>%
  mutate(changes = stringency != dplyr::lag(stringency))

lebanon %>% 
  ggplot(aes(x = t, y = incidence)) + 
    geom_line() + 
    geom_line(aes(y=rollmean(incidence, 7, na.pad=TRUE))) +
    geom_vline(xintercept=lebanon$t[which(lebanon$changes)], linetype=4, colour="red")
```
```{r}
final_data_100 %>%
  mutate(rounded_govt_trust = round(govt_trust)) %>%
  ggplot(aes(x = stringency_change, y = R_est)) +
  geom_point() +
  facet_wrap(vars(rounded_govt_trust))
```
Get the R by govt_trust for changes to see if more trusted govts lock down sooner

```{r}
final_data_100 %>%
  ggplot(aes(x = govt_trust, y = R_est)) +
  geom_point() +
  geom_smooth(method = 'lm')

R_est_trust <- lm(R_est ~ govt_trust, final_data_100)
```


Get the stringency by govt_trust to see if more trusted govts are more stringent.

```{r}
final_data_100 %>%
  ggplot(aes(x = govt_trust, y = stringency_change)) +
  geom_point() +
  geom_smooth(method = 'lm')

string_trust <- lm(stringency_change ~ govt_trust, final_data_100)
```

```{r}
stringency1 <- lm(stringency ~ govt_trust + inc_pop, final_data_100)

summary(stringency1)
```

